---
title: "On the Evolution of Firm Size Distributions"
author: "Woldetsadick Selam Getachew"
date: "Monday, September 15, 2014"
output: html_document
---
<h4,align="left>Replication of findings [A,Paolo & A,Generale (2008)](http://www.jstor.org/discover/10.2307/29729977?uid=3737864&uid=2&uid=4&sid=21104166174021)<sup>1</sup></h4>
<br>
```{r set-options,cache=TRUE}
```
```{r,echo = FALSE,results='hide'}
old.loc <- Sys.getlocale("LC_TIME")
Sys.setlocale(category = "LC_TIME", locale="English")
time <- format(Sys.time(),"%a, %b %d %Y, %X")
version <- R.Version()
varsion <- version[[13]]
old.loc <- Sys.getlocale("LC_TIME")
```

<h1 align="center">Motivation</h1>
<hr width="100%"  noshade size=4>

This work is an attempt at a **replication** of Angelini Paolo and Andrea Generale's 2008 article entitled *On the Evolution of Firm Size Distributions* and published in the American Economic Review<sup>1</sup>.Econometric study for the original article was implemented in SAS statistical analysis software, in this replication R a different statistical analysis software will be used.The goal of this replication work is to indeed replicate findings of the original authors of the article, and extend their results.<br>
The raw data and code books pdf can be found [here](http://www.aeaweb.org/aer/data/mar08/20050397_data.zip) for downloading.<br>
The following analysis was made using the `r time` version of the raw data, and `r varsion` version of R combined with RStudio Desktop v0.98.1056 front.<br> 
<br>
<br>

<h1 align="center">Introduction</h1>
<hr width="100%" noshade size=4>
hereinafter the study

<br>
<br>

<h1 align="center">Loading and pre-processing raw data</h1>
<hr width=100% noshade size=4>
<h4 align="left"> A - Loading the Data</h4>
This chuck of R code uses `dowloader` library to download directly data from the url specified in *url* symbol. The data thus obtained is unzipped using `unzip` function and stored in *ori* symbol. After data is coerced into a matrix aspect and  assigned *mat* symbol, first column - second line of said matrix, corresponding to raw data, is loaded using `read.dta` function of `foreign` library.The raw is therefore named *data* in R.<br>
Also `shell.exec` function is used to open the code book for user automatically. Make sure you have a pdf reader installed.
```{r}
library(foreign)
library(downloader)
setwd("C:/Users/anton_000/Documents/Downloads/Desktop/Replication")
url <- "http://www.aeaweb.org/aer/data/mar08/20050397_data.zip"
download(url,"datasur.dat", mode="wb")
ori <- unzip("datasur.dat")
mat <- matrix(ori)
data <- read.dta(mat[2,1])
shell.exec(file.path(getwd(), "readme.pdf"))
```
<br>
<h4 align="left"> B - Pre-processing the Data</h4>
First a quick look at the names of columns in the data set charged in R environment to compare it with **readme.pdf** listed variables, and also the classes of all variables to match with information in readme file.
```{r}
names <- names(data) #storing column names in "names" vector
classes <- rep(0, times=ncol(data)) # creating vector to store classes of data column
for(i in 1:ncol(data)) {classes[i] <- class(data[,i])} # for each column in data finding class storing it in vector "classes" 
names #displaying names
classes# displaying classes
```
<br>As can be seen above although all variables listed in the readme file are present in our data set, all of them seem to have a numeric class in R. However, variable *anno* should be treated as a variable of **Date class** and variables *ACO*, *AIM*, *SALES*, *sales*, *UTIL*, *UTILN*, *OF*, *IMIM* and *IMTE* should have **class numeric**, *indentif* **class factor**, while *the rest* should have **class integer**.<br>
In the following chunk of code does exactly that.
```{r}
suppressWarnings(for(i in 1:14) {data[,i] <- as.integer(data[,i])}) # changing class of other variables to integer
suppressWarnings(for(i in 23:ncol(data)) {data[,i] <- as.integer(data[,i])}) # changing class of other variables to integer
data$anno <- as.Date(paste(as.character(data$anno),paste("01","01",sep="-"),sep="-"),"%Y-%m-%d") # changing class for anno variable to date
data$identif <- as.factor(data$identif) # indentif number is treated as factor
classes <- rep(0, times=ncol(data)) # creating vector to store classes of data column
for(i in 1:ncol(data)) {classes[i] <- class(data[,i])} # for each column in data finding class storing it in vector "classes" 
classes # displaying classes
```
It can be seen above that classes of variables in the data set are made to match expectations in view of code book. Also note that month and day of observations have been set to default 01-01 because they are unavailable in raw data. <br>
Now that this pre-processing of data is finished, the process of tidying the data and making it "regression" friendly can start. 
<br>
<br>
<h1 align="center">Generating estimation data sets</h1>
<h4 align="center">Transcribing dataset.do and obtaining open9201.dta, closed9201.dta and tempstime_1.dta</h3>
<hr width="100%" noshade size=4>

<h4 align="left"> A - tempstime_1.dta</h4>
The code chunks in the following sub-part of this document loads the Mediocredito Survey & Balance Sheet data containing information for each individual firms for each four years separetely, generates and saves relevant variables used in the original paper.<br>
Data from each different years need slightly adjusted code to process them compared to one another.<br>

<h6 align="left">1 - Creating intermediary data set csur92</h6>
Generating data for firms observed in 1992, each have unique indentifier that they keep over the years.<br>
Here only observations current to 1992 for firms in data set are selected and saved in csur92 data set. Additionally these firms should have a correct observation for number of employees the year before (1991) in order to be able to calculate labor growth current year 1992.<br>
```{r}
csur92 <- subset(data,ind92==1 & dip91!="." & dip91>0)
```
Now relevant variables are created.
```{r}
library(plyr)
csur92$lsize <- data.frame(log(csur92$sales))
csur92$razd <- as.factor(ifelse(csur92$d17_1==3|csur92$d17_2==3|csur92$d17_3==3|csur92$d17_4==3,1,ifelse(csur92$d17_1==9 &csur92$d17_2==9 & csur92$d17_3==9 & csur92$d17_4==9,NA,0)))
csur92$duacq <- as.factor(ifelse(csur92$acqui==1,1,0))
csur92$dusco <- as.factor(ifelse(csur92$scorpo==1,1,0))
csur92$dupav1 <- ifelse(csur92$pav == 1, 1, 0)
csur92$dupav2 <- ifelse(csur92$pav == 2, 1, 0)
csur92$dupav3 <- ifelse(csur92$pav == 3, 1, 0)
csur92$dupav4 <- ifelse(csur92$pav == 4, 1, 0)
csur92$roa <- csur92$util/(csur92$aco+csur92$aim)
csur92$ofut <- csur92$of/(csur92$of+csur92$utiln)
csur92$quoimm <- csur92$imte/(csur92$aco+csur92$aim)
csur92$lsales <- log(csur92$sales)

common <- data.frame(tapply(csur92$ofut, csur92$anno, quantile, probs=.75, na.rm = TRUE))
a <- data.frame(rep(NA, times = (12 - nrow(common))))
names(common)[1] <- "common"
names(a)[1] <- "common"
common <- data.frame(rbind(common,a))
csur92$pofut <- data.frame(ifelse(csur92$anno=="1989-01-01",common[1,1],ifelse(csur92$anno=="1990-01-01",common[2,1],ifelse(csur92$anno=="1991-01-01",common[3,1],ifelse(csur92$anno=="1992-01-01",common[4,1],ifelse(csur92$anno=="1993-01-01",common[5,1],ifelse(csur92$anno=="1994-01-01",common[6,1],ifelse(csur92$anno=="1995-01-01",common[7,1],ifelse(csur92$anno=="1996-01-01",common[8,1],ifelse(csur92$anno=="1997-01-01",common[9,1],ifelse(csur92$anno=="1998-01-01",common[10,1],ifelse(csur92$anno=="1999-01-01",common[11,1],common[12,1]))))))))))))

common <- data.frame(tapply(csur92$quoimm, csur92$anno, quantile, probs=.25, na.rm = TRUE))
b <- data.frame(rep(NA, times = (12 - nrow(common))))
names(common)[1] <- "common"
names(b)[1] <- "common"
common <- data.frame(rbind(common, b))
csur92$pquoimm <- data.frame(ifelse(csur92$anno=="1989-01-01",common[1,1],ifelse(csur92$anno=="1990-01-01",common[2,1],ifelse(csur92$anno=="1991-01-01",common[3,1],ifelse(csur92$anno=="1992-01-01",common[4,1],ifelse(csur92$anno=="1993-01-01",common[5,1],ifelse(csur92$anno=="1994-01-01",common[6,1],ifelse(csur92$anno=="1995-01-01",common[7,1],ifelse(csur92$anno=="1996-01-01",common[8,1],ifelse(csur92$anno=="1997-01-01",common[9,1],ifelse(csur92$anno=="1998-01-01",common[10,1],ifelse(csur92$anno=="1999-01-01",common[11,1],common[12,1]))))))))))))

csur92$duofut <- ifelse(csur92$ofut > csur92$pofut & csur92$ofut != ".",1,ifelse(csur92$ofut==".",".",0))
csur92$dimm <- ifelse(csur92$quoimm < csur92$pquoimm & csur92$pquoimm != ".",1,ifelse(csur92$ofut==".",".",0))

csur92[grep("acqui",colnames(csur92))]=NULL
csur92[grep("scorpo",colnames(csur92))]=NULL
csur92[grep("^pav$",colnames(csur92))]=NULL
csur92 <- csur92[order(csur92$identif),]

```



<br>
<sup>1</sup>Angelini, Paolo, and Andrea Generale. 2008. "On the Evolution of Firm Size Distributions." American Economic Review, 98(1): 426-38.